README

### 2023-07-10 rmd/readme.Rmd
edit: readme

Title: Ecosystem size and complexity are extrinsic drivers of food chain length in branching networks

>>>>

[![DOI](https://zenodo.org/badge/469160066.svg)](https://zenodo.org/badge/latestdoi/469160066)

Title: Ecosystem size and complexity as extrinsic drivers of food chain length in branching networks

Author: Justin Pomeranz, Jacques Finlay, Akira Terui

Journal: Ecosphere
